a and generators

### 2022-04-13 documentos/kraus.tex
Pequeñas anotaciones

% }}}
\subsection{Kraus representation} % {{{
To derive the aforementioned implementations, we exploit the existence of the
PCEGs and their \textit{Kraus representation} (or operator-sum representation)
which, for an arbitrary channel $\mcE$,  reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{},
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
% The Kraus operators corresponding to one single qubit PCEs are 
% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
% % \begin{equation}
% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
% % \label{eq:kraus:PCE}
% % \end{equation}
% corresponding to the operation that leaves the component $\sigma_i$
% invariant~\cite{nielsen_chuang_2011}.
Inspection of the Kraus operators of two qubit PCEG leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are 
\begin{equation}
K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
% \left\{\openone/\sqrt2, 
% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
\label{eq:kraus:PCE}
\end{equation}
since the Kraus operators corresponding to one single qubit PCEs are 
$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
corresponding to the operation that leaves the component $\sigma_\alpha$
invariant~\cite{nielsen_chuang_2011}.

We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce a PCE. 
Notice that 
% \begin{equation}
$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$,
% \label{}
% \end{equation}
which in turn imply that 
\begin{equation}
\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
\label{eq:sigma_property}
\end{equation}
% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on an $N$ qubit system:
\begin{align}
\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}.
\end{align}
However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
except for the first row, half of the matrix elements of each row is $+1$ and 
half $-1$, which implies that the channel is a PCEG.

@@

Notice also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
leads to different channels. This follows from the fact that if two channels were
the same, this would imply that the matrix representation of the corresponding
superoperator of $\rho \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$
% $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$ 
% \ddnote{en este punto me confundio bastante esta notacion, contrapropongo $\rho
% \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$, que es una notación que
% hemos venido usando.}
would have to be the same which is clearly false. Since there are $4^n$ different 
$\vec \alpha$, this implies that all PCEG (plus the identity map) are in one to 
one correspondence.

>>>>

% }}}
\subsection{Kraus representation} % {{{
To derive the aforementioned implementations, we exploit the existence of the
PCEGs \janote{introducimos esta notación antes?} and their \textit{Kraus representation} (or operator-sum representation)
which, for an arbitrary channel $\mcE$,  reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{},
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
% The Kraus operators corresponding to one single qubit PCEs are 
% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
% % \begin{equation}
% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
% % \label{eq:kraus:PCE}
% % \end{equation}
% corresponding to the operation that leaves the component $\sigma_i$
% invariant~\cite{nielsen_chuang_2011}.
Inspection of the Kraus operators of two qubit PCEGs leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are 
\begin{equation}
K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
% \left\{\openone/\sqrt2, 
% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
\label{eq:kraus:PCE}
\end{equation}
since the Kraus operators corresponding to one single qubit PCEs are 
$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
corresponding to the operation that leaves the component $\sigma_\alpha$ \janote{$r_0$ and $r_\alpha$}
invariant~\cite{nielsen_chuang_2011}.

We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce \janote{are indeed} a PCE. 
Notice that 
% \begin{equation}
$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$ \janote{[see \Eref{eq:1}]},
% \label{}
% \end{equation}
which in turn imply that 
\begin{equation}
\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
\label{eq:sigma_property}
\end{equation}
% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on a $N$-qubit system:
\begin{align}
\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}.
\end{align}
However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
by Kraus operators  \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
except for the first row, half of the matrix elements of each row is $+1$ and 
half $-1$, which implies that the channel is a PCEG.

@@

Notice also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
leads to different channels. This follows from the fact that if two channels were
the same, this would imply that the matrix representation of the corresponding
superoperator of $\rho \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$
% $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$ 
% \ddnote{en este punto me confundio bastante esta notacion, contrapropongo $\rho
% \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$, que es una notación que
% hemos venido usando.}
would have to be the same, which is clearly false. Since there are $4^n$ different 
$\vec \alpha$, this implies that all PCEG (plus the identity map) are in one to 
one correspondence.
